---
title: "R Notebook"
output: html_notebook
---

First up: we load our libraries and our data:

```{r}

library(ggplot2)
library(data.table)
library(knitr)
library(kableExtra)
require(ordinal)


df <- data.table(read.csv("ux_table.csv"))

```

Now a few fields that we'll use throughout our EDA:

```{r}

df$totalCompletionTime <- df$timeToCompleteA + df$timeToCompleteB + df$timeToCompleteC

df$satisfaction <- ifelse( df$satisfactionWithWebsite > 0, df$satisfactionWithWebsite, ifelse(df$satisfactionWithAPS > 0, df$satisfactionWithAPS, df$satisfactionWithRepresentative))

```

What's our initial posited causal diagram?

```{r}
library(ggdag)
library(ggplot2)

relations <- dagify(
  Score ~ Time,
  Time ~ Help + Des + Prev + APS,
  exposure = "Des",
  outcome = "Score"
) 

tr <- tidy_dagitty(relations)

#ggdag(relations)

tr <- dplyr::mutate(tr, color = ifelse(name == "Score", "Outcomes", "Variables"))


tr %>%
  node_parents("Score") %>%
  node_children("Help") %>%
  ggplot(aes(x = x, y = y, xend = xend, yend = yend, color = color)) +
    geom_dag_point() +
    geom_dag_edges() +
    geom_dag_text(col = "white") +
    theme_dag() +
    png("first_dag.png", width=3000, height=2000, res = 600) #output to png so it looks better

```

What's our completion time look like?

```{r}
completionTimes <- df[startedOnWebsite == 1, mean(totalCompletionTime), redesign]
knitr::kable( completionTimes[order(redesign)], "html", col.names = c("Redesigns", "Completion Time"), align = "cc", caption = "Total Completion Time By Number of Redesigned Tasks") %>% kable_styling()
```

Group by number of redesigns, split by previous user or not, completion times look any better?

```{r}

webusers <- df[df$satisfactionWithWebsite > 0,
               avgCompletion := mean(totalCompletionTime), 
               by=.(redesign, previousWebsiteUser)]

webusers <- na.omit (webusers, "avgCompletion") 

useStats <- webusers[, setdiff(names(webusers), c("avgCompletion", "redesign", "previousWebsiteUser")) := NULL][]
useStats <- useStats[!duplicated(useStats[, c("redesign", "previousWebsiteUser"),])]

setorder(useStats, cols = "redesign", "previousWebsiteUser")
ggplot(useStats, 
       aes(x=redesign, y=avgCompletion, fill=factor(redesign))
       ) + 
  geom_bar(aes(y = avgCompletion, fill = factor(..x..)), stat = "identity") +
  facet_grid (useStats$previousWebsiteUser) + 
  xlab("Number of Redesigns") + 
  ylab("Completion Times") +
  ggtitle("Change in completion time for Previous Users and New Users")

```

How about times for previous site users?

```{r}

ggplot(df[previousWebsiteUser == 1 & redesign == 0,], 
       aes(x=totalCompletionTime)
       ) + 
  geom_histogram(aes(y =..count..), fill = "blue", colour="white", bins = 30) +
  xlab("Completion Times") + 
  ylab("Number of Users") +
  ggtitle("Previous Users With No Redesign")


```

Now we can look at how new users differ from previous users when there's 3 redesigns:

```{r}

min(df$timeToCompleteA)

ggplot(df[redesign == 3,], 
       aes(x=totalCompletionTime)
       ) + 
  geom_histogram(aes(y = (..count..)/sum(..count..)), bins = 20, fill = "blue", colour="white",) +
  facet_grid (df[redesign == 3,]$previousWebsiteUser) + 
  xlab("Completion Times") + 
  ylab("Number of Users") +
  ggtitle("Distribution of completion times for Previous Users and New Users")


```


How's our user satisfaction?


```{r}
ggplot(df[df$satisfactionWithWebsite > 0,], aes(x=satisfactionWithWebsite, fill="blue")) +
                        geom_bar(aes(y = ..prop..), stat="count") +
                        ylab("Rating by Percentage of Users")
```

Not great!

How about the satisfaction between new users and previous users?


```{r}
ggplot(df[df$satisfactionWithWebsite > 0,], aes(x=satisfactionWithWebsite, fill=previousWebsiteUser)) +
                        theme(legend.position = "right") +
                        geom_bar(aes(y = ..prop.., fill = factor(previousWebsiteUser)), stat="count", position="dodge") +
                        scale_x_discrete(breaks=seq(1, 5, 1))

```

Are they statistically significant?

```{r}
ks.test(df[df$previousWebsiteUser == 1,]$satisfactionWithWebsite, df[df$previousWebsiteUser == 0,]$satisfactionWithWebsite)
```

How about a distribution of ratings based on number of redesigns?

```{r}
ggplot(df[df$startedOnWebsite == 1 & df$satisfactionWithWebsite > 0,], 
       aes(x=df[df$startedOnWebsite == 1  & df$satisfactionWithWebsite > 0,]$satisfactionWithWebsite,
           fill=df[df$startedOnWebsite == 1  & df$satisfactionWithWebsite > 0,]$satisfactionWithWebsite)
       ) + 
  geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count") + 
  scale_x_discrete(labels=scales::percent) +
  facet_grid (df[df$startedOnWebsite ==  1 & df$satisfactionWithWebsite > 0,]$redesign) + 
  xlab("Number of Redesigns") + 
  ylab("Distribution of Ratings") + 
  coord_flip() + 
  scale_fill_discrete("Rating")
```


How about a correlation matrix?

```{r}

library(corrplot)
library(ggcorrplot)

cor.mtest <- function(mat, ...) {
    mat <- as.matrix(mat)
    n <- ncol(mat)
    p.mat<- matrix(NA, n, n)
    diag(p.mat) <- 0
    for (i in 1:(n - 1)) {
        for (j in (i + 1):n) {
            tmp <- cor.test(mat[, i], mat[, j], ...)
            p.mat[i, j] <- p.mat[j, i] <- tmp$p.value
        }
    }
  colnames(p.mat) <- rownames(p.mat) <- colnames(mat)
  p.mat
}

p.mat <- cor.mtest(df[,c("redesign", "previousWebsiteUser", "totalCompletionTime", "transferredToAPS", "satisfactionWithWebsite", "usedHelp"),])

corr <- cor(df[,c("redesign", "previousWebsiteUser", "totalCompletionTime", "transferredToAPS", "satisfactionWithWebsite", "usedHelp"),])
col <- colorRampPalette(c("#BB4444", "#EE9988", "#FFFFFF", "#77AADD", "#4477AA"))

corrplot(corr, method="color", col=col(200),  
          type="upper", order="hclust", 
         addCoef.col = "black", # Add coefficient of correlation
         tl.col="black", tl.srt=45, #Text label color and rotation
         # Combine with significance
         p.mat = p.mat, sig.level = 0.01, insig = "blank", 
         # hide correlation coefficient on the principal diagonal
         diag=FALSE 
         )

```

Let's update our DAG

```{r}

relations <- dagify(
  Score ~ Help + Prev + Time,
  Help ~ Des + Prev,
  APS ~ Des + Help + Time,
  exposure = "Des"
) 

tr <- tidy_dagitty(relations)

tr <- dplyr::mutate(tr, color = ifelse(name == "Score" | name == "APS", "Outcomes", "Variables"))

tr %>%
  node_parents("Help") %>% node_parents("Des") %>%
  node_children("APS") %>% node_children("Score") %>%
  ggplot(aes(x = x, y = y, xend = xend, yend = yend, color=color)) +
    geom_dag_point() +
    geom_dag_edges() +
    geom_dag_text(col = "white") +
    theme_dag() +
    png("second_dag.png", width=3000, height=2000, res = 600)

```

Now to make a model:


```{r}

satisfactionModel <- lm( satisfactionWithWebsite ~ usedHelp * redesign + as.factor(previousWebsiteUser), df[satisfactionWithWebsite > 0,] )
summary(satisfactionModel)

```