---
title: "R Notebook"
output: html_notebook
---

```{r}
library(ggplot2)
library(data.table)
library(knitr)
library(kableExtra)
library(ordinal)
library(MASS)
library(DescTools)
library(rcompanion)
library(lmtest)
library(flexmix)
library(diptest)

df <- data.table(read.csv("ux_table.csv"))

```

First, let's engineer some features!

```{r}
df$totalCompletionTime <- df$timeToCompleteA + df$timeToCompleteB + df$timeToCompleteC

df$satisfaction <- ifelse( df$satisfactionWithWebsite > 0, df$satisfactionWithWebsite, ifelse(df$satisfactionWithAPS > 0, df$satisfactionWithAPS, df$satisfactionWithRepresentative))

df$satisfactionBin <- ifelse( df$satisfaction > 3, 1, 0)

```

Do we have multimodality?

```{r}
dip.test(df$satisfaction)
```

Where are our two modes?

```{r}
library(BSDA)
dstamp <- density(df$satisfaction, bw=1, kernel = "gaussian")
chng <- cumsum(rle(sign(diff(dstamp$y)))$lengths)
plot(dstamp, main="Detected Modes of Ratings")
abline(v = dstamp$x[chng[seq(1,length(chng),2)]])
```

One more check for multimodality:

```{r}
library(LaplacesDemon)
is.multimodal(df$satisfaction)
```

Let's take a look at the satisfaction based on redesign and help

```{r}

library(lattice)

histogram(~ satisfaction | redesign,
          data=df,
          layout=c(1,4)      #  columns and rows of individual plots
          )

```

Let's try a cumulative link model. Does it do any better?

```{r}

### build the cumulative link model
m <- clm(as.factor(satisfactionBin) ~ as.factor(usedHelp) + as.factor(redesign), 
         data = df[satisfactionWithWebsite > 0,], 
         Hess=TRUE)

### view a summary of the model
summary(m)

### get the coefficients
(ctable <- coef(summary(m)))

### confint
ci <- confint(m)
```

```{r}


### build a null model
model.null <- clm(as.factor(satisfactionWithWebsite) ~ 1, data = df[satisfactionWithWebsite > 0,])

### now anova it and see if our model is better than a blank model
anova(m, model.null)

### now how does our model do against an empty model?
print(1 - m$logLik/model.null$logLik )


```
So we're onto something in our satisfaction, but that doesn't express that satisfaction AND transferring express ease of use.

Let's get into the LCA and look at our classes for people who had no redesigns.


```{r}

library(poLCA)

#requires recoding
polca_recode <- df[startedOnWebsite == 1 & transferredToRep == 0,]
polca_recode$transferredToAPS <- 2 - polca_recode$transferredToAPS
polca_recode$redesign <- polca_recode$redesign + 1
polca_recode$usedHelp <- polca_recode$usedHelp + 1
polca_recode$previousWebsiteUser <- polca_recode$previousWebsiteUser + 1

no_redesign <- poLCA(
                cbind(satisfaction, transferredToAPS, usedHelp) ~ 1,
                nclass=2,
                data=polca_recode[redesign == 1,],
                nrep=1,
                na.rm=F,
                graphs=T,
                maxiter = 100000
             )

```

Now let's look at our classes for people who had all the redesigns.


```{r}
redesign_mod <- poLCA(
                cbind(satisfaction, transferredToAPS, usedHelp) ~ 1,
                nclass=2,
                data=polca_recode[redesign == 4,],
                nrep=1,
                na.rm=F,
                graphs=T,
                maxiter = 100000
             )

```

Let's make a few poLCA objects with multiple classes to make sure 2 captures it correctly:

```{r}

polca_all2 <- poLCA(
                cbind(satisfaction, transferredToAPS, usedHelp, redesign) ~ 1,
                nclass=2,
                data=polca_recode,
                nrep=1,
                na.rm=F,
                graphs=F,
                maxiter = 100000
             )

polca_all3 <- poLCA(
                cbind(satisfaction, transferredToAPS, usedHelp, redesign) ~ 1,
                nclass=3,
                data=polca_recode,
                nrep=1,
                na.rm=F,
                graphs=F,
                maxiter = 100000
             )

polca_all4 <- poLCA(
                cbind(satisfaction, transferredToAPS, usedHelp, redesign) ~ 1,
                nclass=4,
                data=polca_recode,
                nrep=1,
                na.rm=F,
                graphs=F,
                maxiter = 100000
             )



polca_entropy <- function (p) sum( -p * log(p) )

error_prior <- polca_entropy(polca_all2$P) # class proportions model 2
error_post <- mean(apply(polca_all2$posterior,1, polca_entropy), na.rm = TRUE)

round(((error_prior-error_post) / error_prior),3)

error_prior <- polca_entropy(polca_all3$P) # class proportions model 2
error_post <- mean(apply(polca_all3$posterior,1, polca_entropy), na.rm = TRUE)

round(((error_prior-error_post) / error_prior),3)

error_prior <- polca_entropy(polca_all4$P) # class proportions model 2
error_post <- mean(apply(polca_all4$posterior,1, polca_entropy), na.rm = TRUE)

round(((error_prior-error_post) / error_prior),3)


```

```{r}
polca_all <- poLCA(
                cbind(satisfaction, transferredToAPS, usedHelp) ~ redesign,
                nclass=2,
                data=polca_recode,
                nrep=1,
                na.rm=F,
                graphs=F,
                maxiter = 100000
             )


```



```{r}
redesign_mat <- cbind(1,c(1:4))
exb <- exp(redesign_mat %*% polca_all$coeff)
class_likelihoods <- (cbind(1,exb) / (1+rowSums(exb)))

lca_df <- data.frame(
  redesigns=c(c(1:4),c(1:4)), 
  class=c(rep(1,4),rep(2,4)), 
  likelihood=c(class_likelihoods[,1], class_likelihoods[,2])
)

ggplot(data=lca_df, aes(x=redesigns, y=likelihood, group=as.factor(class))) +
  geom_line(aes(color=as.factor(class))) +
  geom_point(aes(color=as.factor(class))) +
  labs(x="Number of Redesigns", y="Likelihood of Latent Class Membership") +
  scale_color_discrete(name="Latent Classes", labels=c('Ease of use: no', 'Ease of use: yes'))
```